\documentclass[a4paper, 12pt]{article}
\input{prefix.tex}%
\input{symbols.tex} 

\title{Wage Estimation}
\author{Kai-Jyun Wang\thanks{National Taiwan University, Department of Economics. Student ID: B11303072.}}
\date{Spring 2025}

\begin{document}

\maketitle

\section{Model Specification}
Let $y^*_t$ be the latent log wage at time $t$ and $a_t$ be the age at time $t$. $d_t$ 
is the dummy for working. The specification of the model is as follows: 
\begin{align*}
    y^*_t &= f(a_t;\beta) + \epsilon_t, \quad \epsilon_t \sim N(0, \sigma_t^2) \\
    \epsilon_t &= \rho\epsilon_{t-1} + \nu_t, \quad \nu_t \sim N(0, \sigma_\nu^2) \\
    d_t &= \mathds{1}\brc{y_t^* \geq g(a_t,z_t;\gamma) + \eta_t}, \quad \eta_t \sim N(0, \sigma_\eta^2) \\ 
    y_t &= y^*_t \times d_t. 
\end{align*}
We take the assumption that $\eta$ and $\epsilon$ are independent. The $\sigma_t^2$ must 
obey that $\sigma_t^2 = \rho^2 \sigma_{t-1}^2 + \sigma_\nu^2$ for $t > 1$. 
Suppose $a_1$ is the first age that enters the labor market. We need to 
estimate the variance of the first period in the data, $\sigma_1^2$. $z_t$ indicates whether 
or not the individual has a child at time $t$.  

\section{Estimation Procedure}
\subsection{A Less Efficient Method}
\begin{enumerate}
    \item For $t = 1$, consider the contemporary log likelihood 
    \begin{equation*}
        \begin{split}
            L_c(\beta_t,\gamma_t,\sigma_t,\sigma_{\eta,t}) &= \sum_{i=1}^N d_i\sbrc{\log\Phi\pth{\frac{y_t - g(a_t,z_t;\gamma_t)}{\sigma_\eta}} + \log\phi\pth{\frac{y_t - f(a_t;\beta_t)}{\sigma_t}} - \log\sigma_t} \\
            &\qquad + (1 - d_i)\log\pth{1 - \Phi\pth{\frac{f(a_t;\beta_t) - g(a_t,z_t;\gamma_t)}{\sqrt{\sigma_t^2 + \sigma_\eta^2}}}},
        \end{split}
    \end{equation*}
    where $\Phi$ and $\phi$ are the cumulative distribution function and the probability 
    density function of the standard normal distribution, respectively. Estimate the 
    $\beta$ for period $t = 1$ by maximizing the contemporary log likelihood with the first 
    period data.  
    \item Using the estimated $\beta$ in first step, compute the residuals $y_t^* - f(a_t;\beta)$. 
    Regress the residuals on the lagged residuals without intercept to estimate $\rho$ and $\sigma_\nu$. 
\end{enumerate}
Estimate the $\beta,\gamma,\sigma_1,\sigma_\eta$ for male and female separately. 

\section{Some Notes}
\begin{itemize}
    \item The specification of $g$ is non-parametric. $g(a_t,z_t;\gamma) = \gamma_{a_t,z_t}$. Each possible 
    combination of $a_t$ and $z_t$ corresponds to a $\gamma_{a_t,z_t}$.
    \item Try different specifications of $f$, for instance, quadratic, cubic, or quartic. 
    \item Estimate the naive model first, i.e., regress $y_t$ on $f(a_t;\beta)$ and use 
    the coefficients as initial values for the $\beta$ and $\gamma$.
\end{itemize}

%\bibliographystyle{apacite}
%\bibliography{final}
\end{document}